Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-03-02 Report/ieee_journal.tex
Merge remote-tracking branch 'origin/revision_tsp_1' into revision_tsp_1
Conflicts:
	Report/ieee_journal.dvi
	Report/ieee_journal.log
	Report/ieee_journal.pdf
	Report/ieee_journal.synctex.gz
	Report/ieee_journal.tex

\title{Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems}
\author{
	\IEEEauthorblockN{Ganesh Venkatraman \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland. Part of this work is presented in ICASSP 2014.}, Antti T\"{o}lli \IEEEmembership{Member,~IEEE}, Le-Nam Tran \IEEEmembership{Member,~IEEE}, and Markku Juntti \IEEEmembership{Senior Member,~IEEE}}\thanks{The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi).}}

@@

\subsection{Average Backlogged Packets Over Slots} \label{time-correlated}
\review{\input{time_correlated}}

>>>>

\title{Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems}
\author{
	\IEEEauthorblockN{Ganesh Venkatraman$^\dagger$ \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland. Part of this work is presented in ICASSP 2014.}, Antti T\"{o}lli$^\dagger$ \IEEEmembership{Senior Member,~IEEE}, Le-Nam Tran$^\ddagger$ \IEEEmembership{Member,~IEEE}, and Markku Juntti$^\dagger$ \IEEEmembership{Senior Member,~IEEE}}\thanks{
	$^\dagger$The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, markku.juntti\}@ee.oulu.fi)}\thanks{$^\ddagger$The author is with the Department of Electronic Engineering, Maynooth University, Maynooth, Co. Kildare, Ireland, (e-mail:ltran@eeng.nuim.ie}}

@@

\subsection{Queue Deviations over Multiple Transmission Slots} \label{time-correlated}
\review{\input{time_correlated}}

### 2015-03-02 Report/review_comments.tex
included antti comments
Merge remote-tracking branch 'origin/revision_tsp_1' into revision_tsp_1
Conflicts:
	Report/ieee_journal.dvi
	Report/ieee_journal.log
	Report/ieee_journal.pdf
	Report/ieee_journal.synctex.gz
	Report/ieee_journal.tex

\subsection{Reveiwer Comments - \me{1}}

@@

\resp We thank the reviewer for reading the paper and providing the comments. The response for the reviewer questions are made in line.

\subsection*{Detailed Comments}  
\cmnt{1} In Section II.B, please provides more justifications for the problem formulation in (6). For example, the Queue weighted sum rate maximization (Q-WSRM) is throughput optimal, i.e., if there exists a scheme which can make all queues stable, then the Q-WSRM can also do this. How about the proposed formulation in (6)? Is it also throughput optimal?

@@

\subsection*{Reveiewer comments - \me{2}}

@@

\subsection*{Reveiewer comments - \me{3}}

@@

\subsection*{Reveiewer comments - \me{4}}

@@

\resp We thank the reviewer for We have updated the proof for convergence in a separate section on Appendix \ref{sec-3.5}.

@@

\resp We thank the reviewer for pointing out the missing information. We have included a figure on the number of backlogged packets over a period of time in Section \ref{time-correlated}.

@@

\resp We agree with the reviewer. We have updated the manuscript with more details.

@@

\resp We thank the reviewer for pointing out the misinterpretation of the text. We have included the statement accordingly in the introduction.

\cmnt{5a} - p. 1, col. 1, row 42: "userss"

\resp Modified.

\cmnt{5b} - p. 1, col. 2, row 18: the precoders are used \_implicitly\_ as decision variables. This is the whole point, to avoid explicitly modeling the hard decisions in the optimization, and instead do soft decisions during the iterations, and then finally hard decisions after convergence.

\resp We thank the reviewer for the insightful comment on the proposed approach. We have modified the text accordingly.

\cmnt{5c} - p. 1, col. 2, row 33: Which chapter in [2] is referred to? With a quick look-through of the table of contents, I can't find and chapter or section treating the SCA method?

\resp We understand the reviewer's concern. We have provided the valid reference for the SCA scheme.

\cmnt{5d} - p. 2, col. 2, row 36: Write $\text{rank}(.)$ and $\min$ instead

\resp Changed.

\cmnt{5e} - p. 3, col. 1, row 26: It would be more clear to explicitly write out the dependence of $\mathbf{M}$ and $\mathbf{W}$ in $\tilde{v}$ here

\resp We thank the reviewer for the concern on the grouped variable. We have modified the expressions accordingly.

\cmnt{5f} - p. 3, col. 2, row 26: Which general MIMO-OFDM problem are you talking about here, and what is combinatorial about it? Is it the problem of selecting users to be served on orthogonal subcarriers? There is nothing inherently combinatorial over the problem in (6) as far as I can tell, as the beamformers are used as soft decision variables.

\resp We thank the reviewer for the comment. We have removed the word "combinatorial" from the text.

\cmnt{5g} - p. 4, col. 2, row 40: "In fact, (5) provides similar expression of ..." This sentence is very hard to understand.

\resp It is restructured to include additional details.

\cmnt{5h} - (16d): suggest your write out the power constraints here, in order to be faster be able to interpret the optimization problem. There is hardly any spaced saved by referring back to (6b).

\resp Agreed.

\cmnt{5i} - p. 5, col. 1, rows 27-30: Here you might want to quickly mentioned how one could show the NP-hardness of (16).

\resp We have updated the NP hardness discussion in the revised version.

\cmnt{5j} - p. 5, col. 1, row 50: "According to the SCA method...". I am not sure exactly how you define "\_the\_ SCA method"? Clarify or cite the definition.

@@

\cmnt{5k} - p. 5, col. 2, row 31: Here is a case where it makes sense to reference earlier optimization constraints. However, are (19d) and (18) not the same??

@@

\cmnt{5l} - p. 5, col. 2, row 51: Slightly confusing with the notation between the iterates in (21b) and the MMSE filter in (22b).

@@

\cmnt{5m} - p. 6, col. 1, row 9: You might want to add somewhere that (22b) can be used instead of the fixed-point of (21b), since the scaling of the receive filters do not matter in the SINRs. However, does it affect the convergence of the algorithm?

@@

\cmnt{5n} - p. 6, col. 2, rows 8-10: I don't fully understand the reasoning on the relation between the constraint sets in the different iterations. Why is this the case?

@@

\cmnt{5o} - p. 7, col. 1, row 35: Just because a problem is convex does not mean that it has a unique solution. (Although it seems to me that (26) should have a unique solution.) Is the problem in (26) strictly convex?

@@

\cmnt{5p} - Table 1: "backpreassure"

@@

\cmnt{5q} - p. 11, col. 1, row 56: "performances". I'm not sure this is a countable noun.

@@

>>>>

\section*{Reveiwer Comments - \me{1}}

@@

\begin{itemize}

\cmnt{1} In Section II.B, please provides more justifications for the problem formulation in (6). For example, the Queue weighted sum rate maximization (Q-WSRM) is throughput optimal, i.e., if there exists a scheme which can make all queues stable, then the Q-WSRM can also do this. How about the proposed formulation in (6)? Is it also throughput optimal?

@@

\end{itemize}

\section*{Reveiewer comments - \me{2}}

\begin{itemize}

@@

\end{itemize}

\section*{Reveiewer comments - \me{3}}

\begin{itemize}

@@

\end{itemize}

\section*{Reveiewer comments - \me{4}}

\begin{itemize}

@@

\resp We understand the reviewer concern on the lack of rigorous convergence proof for the proposed JSFRA approach. We have presented a rigorous convergence proof for the proposed algorithm in Appendix B on page 14. We have included the reference suggested by the reviewer in [34].

@@

\resp We understand the concern raised by the reviewer. In the current paper, we are discussing on the precoder design to minimize the number of backlogged packets in the system at a given time. Since the greedy approach performed at each instant minimizes the number of backlogged packets on an average, we emphasized on the precoder design based on the current knowledge of the channel state information. We have included Section V-C in page 13 to discuss on the performance of the JSFRA scheme for different \me{\ell_q} norm over multiple time slots. Plots comparing the average number of backlogged packets for different schemes at each instant and the number of queued packets remained in the system after each transmission instant are provided in Fig. 4.

@@

\resp We agree with the reviewer comment. We have shortened the discussions on the distributed approaches and discussed the convergence proof of the decentralized algorithm in Section IV-C page 8. We have included the information on what each network entity knows in page 7, col. 2 last paragraph. We have included the type of duplexing scheme adopted in the model, \textit{i.e}, TDD system, in the system description in Section II, last paragraph.

@@

\resp We agree with the reviewer point. We have included the note on the space-frequency terminology in the introduction section on page 2, col. 2, line 2-4.

\cmnt{5} Please see the itemized questions

\begin{itemize}

\cmnts{a} - p. 1, col. 1, row 42: "userss"

\resp Corrected in the revised manuscript in Section I on page 1, col. 1, line 2.

\cmnts{b} - p. 1, col. 2, row 18: the precoders are used \_implicitly\_ as decision variables. This is the whole point, to avoid explicitly modeling the hard decisions in the optimization, and instead do soft decisions during the iterations, and then finally hard decisions after convergence.

\resp We thank the reviewer for highlighting the important point. We have included the statement in the revised manuscript on Section I, page 1, col. 2, line 5-14.

\cmnts{c} - p. 1, col. 2, row 33: Which chapter in [2] is referred to? With a quick look-through of the table of contents, I can't find and chapter or section treating the SCA method?

\resp We apologize for the wrong reference. We have updated the manuscript to include the proper reference on SCA with [2,3,7,35].

\cmnts{d} - p. 2, col. 2, row 36: Write $\text{rank}(.)$ and $\min$ instead

\resp We have updated the revised manuscript with the reviewer suggestions on page 2, col. 2, second paragraph in Section II.

\cmnts{e} - p. 3, col. 1, row 26: It would be more clear to explicitly write out the dependence of $\mathbf{M}$ and $\mathbf{W}$ in $\tilde{v}$ here

\resp We removed the matrix representation of the transmit precoders and the receive beamformers from the manuscript to avoid confusion as suggested by the reviewer.

\cmnts{f} - p. 3, col. 2, row 26: Which general MIMO-OFDM problem are you talking about here, and what is combinatorial about it? Is it the problem of selecting users to be served on orthogonal subcarriers? There is nothing inherently combinatorial over the problem in (6) as far as I can tell, as the beamformers are used as soft decision variables.

\resp We thank the reviewer for pointing out the confusion. We have removed the word "combinatorial" from the text to avoid confusion in page 3, col. 2, initial sentence in Section III.

\cmnts{g} - p. 4, col. 2, row 40: "In fact, (5) provides similar expression of ..." This sentence is very hard to understand.

\resp We have rephrased the sentence to avoid difficulty in the understanding. The manuscript is updated with the revised text on page 4, col. 2, first paragraph in Section III.B.

\cmnts{h} - (16d): suggest your write out the power constraints here, in order to be faster be able to interpret the optimization problem. There is hardly any spaced saved by referring back to (6b).

\resp We have updated the manuscript with the explicit power constraint (16d).

\cmnts{i} - p. 5, col. 1, rows 27-30: Here you might want to quickly mentioned how one could show the NP-hardness of (16).

\resp We have included the sentence on the NP-hardness

\cmnts{j} - p. 5, col. 1, row 50: "According to the SCA method...". I am not sure exactly how you define "\_the\_ SCA method"? Clarify or cite the definition.

@@

\cmnts{k} - p. 5, col. 2, row 31: Here is a case where it makes sense to reference earlier optimization constraints. However, are (19d) and (18) not the same??

@@

\cmnts{l} - p. 5, col. 2, row 51: Slightly confusing with the notation between the iterates in (21b) and the MMSE filter in (22b).

@@

\cmnts{m} - p. 6, col. 1, row 9: You might want to add somewhere that (22b) can be used instead of the fixed-point of (21b), since the scaling of the receive filters do not matter in the SINRs. However, does it affect the convergence of the algorithm?

@@

\cmnts{n} - p. 6, col. 2, rows 8-10: I don't fully understand the reasoning on the relation between the constraint sets in the different iterations. Why is this the case?

@@

\cmnts{o} - p. 7, col. 1, row 35: Just because a problem is convex does not mean that it has a unique solution. (Although it seems to me that (26) should have a unique solution.) Is the problem in (26) strictly convex?

@@

\cmnts{p} - Table 1: "backpreassure"

@@

\cmnts{q} - p. 11, col. 1, row 56: "performances". I'm not sure this is a countable noun.

@@

\end{itemize}

\end{itemize}
